Modular flow and holographic entanglement entropy in cutoff AdS / \TTbar deformed theory

### 2021-06-22 alpha/CutoffModularFlow/notes.tex
Clean up notes a bit more

%	\item[] In Section 1,

@@

	\item We look at the flow at constant cutoff $z = z_c$, which has non-trivial $\pdd{z}$ component, which in turn leads to a violation of the $2\pi$ periodicity for $\xi$ along the horizon. This could be related to the violation of boosted strong subadditivity (boosted SSA) in \cite{Lewkowycz:2019xse}.

@@

	\item We try to obtain the entanglement entropy using the modular flow at the \mbox{codim-2} cutoff surface, using the \textit{effective inverse temperature $\beta(x)$} introduced in \cite{Wong:2013gua,Cardy:2016fqc}, which relates the entanglement entropy to some thermal entropy. \sidenote{[relation with partial entanglement entropy?]}

	\item \sidenote{We should look at the boosted interval.}

%	\item[] In Section 2,

	\item We map the the modular flow in the Poincar\'e $\mrm{AdS}_3$ vacuum to the BTZ background, and compute the entanglement entropy as gravitational charge.

	\item We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}. This gives a finite temperature generalization of the result of \cite{Lewkowycz:2019xse}.

@@

review TTbar and cutoff AdS

\subsection{black spectrum from gravitional charges}
	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.

@@

	\noindent\hrulefill

	On the other hand, gravitational entropy is the Noether charge $Q_\xi$ associated with some horizon generator $\xi$. In the case of entanglement entropy between a simple interval and its complement, we've found its corresponding modular flow in the bulk, which is precisely the horizon generator of the Rindler patch. We then aim to compute the charge variation using the covariant formula:
	\begin{equation}
		\var{Q}_{\xi} [\var{g}, g]
		= \int_{\pd\Sigma}
			\chi_\xi
		= \frac{1}{16 \pi G}
			\int_{\pd\Sigma}
			\sqrt{|g|} \dd{x}^{\alpha}
				\varepsilon_{\alpha\mu\nu}\,
				k_\xi^{\mu\nu} [\var{g}, g]
	\end{equation}
	\begin{equation}
	\begin{aligned}
		k_\xi^{\mu\nu}[\var g, g]
		= \frac{1}{2} \Big \{
		& \xi^{\nu}\nabla^{\mu} \var g^{\alpha}{}_{\alpha}
		- \xi^{\nu} \nabla_{\alpha} \var g^{\alpha\mu}
		+ \xi_{\alpha} \nabla^{\nu} \var g^{\alpha\mu}  \\
		&+ \frac{1}{2} \var g^{\alpha}{}_{\alpha} \nabla^{\nu} \xi^{\mu}
		- \frac{1}{2} \var g^{\nu\alpha} \nabla_{\alpha}\xi^{\mu}
		+ \frac{1}{2} \var g^{\nu\alpha} \nabla^{\mu} \xi_{\alpha} \\
		&- (\mu \leftrightarrow \nu) \Big \}
	\end{aligned}
	\label{kdef}
	\end{equation}
	However, to compute $\var{Q}$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions. There is no free parameter in Poincar\'e $\mrm{AdS}_3$, unless we turn on temperature; namely we have to start with the BTZ geometry.

@@

	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.

	Gravitational entropy is the Noether charge $Q_\xi$ associated with some horizon generator $\xi$. In the case of entanglement entropy between a simple interval and its complement, we've found its corresponding modular flow in the bulk, which is precisely the horizon generator of the Rindler patch. We then aim to compute the charge variation using the covariant formula:
	\begin{equation}
		\var{Q}_{\xi} [\var{g}, g]
		= \int_{\pd\Sigma}
			\chi_\xi
		= \frac{1}{16 \pi G}
			\int_{\pd\Sigma}
			\sqrt{|g|} \dd{x}^{\alpha}
				\varepsilon_{\alpha\mu\nu}\,
				k_\xi^{\mu\nu} [\var{g}, g]
	\end{equation}
	\begin{equation}
	\begin{aligned}
		k_\xi^{\mu\nu}[\var g, g]
		= \frac{1}{2} \Big \{
		& \xi^{\nu}\nabla^{\mu} \var g^{\alpha}{}_{\alpha}
		- \xi^{\nu} \nabla_{\alpha} \var g^{\alpha\mu}
		+ \xi_{\alpha} \nabla^{\nu} \var g^{\alpha\mu}  \\
		&+ \frac{1}{2} \var g^{\alpha}{}_{\alpha} \nabla^{\nu} \xi^{\mu}
		- \frac{1}{2} \var g^{\nu\alpha} \nabla_{\alpha}\xi^{\mu}
		+ \frac{1}{2} \var g^{\nu\alpha} \nabla^{\mu} \xi_{\alpha} \\
		&- (\mu \leftrightarrow \nu) \Big \}
	\end{aligned}
	\label{kdef}
	\end{equation}
	However, to compute $\var{Q}$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions. There is no free parameter in Poincar\'e $\mrm{AdS}_3$, unless we turn on temperature; this leads to the BTZ geometry.

>>>>

	\item[] On the field theory side,

	\item Following \cite{Lewkowycz:2019xse,Donnelly:2018bef}, we derive the entanglement entropy for a \TTbar deformed theory, and extend the result to the finite temperature case.

	\item We note that it is possible to generalize the \textit{effective inverse temperature $\beta(x)$} trick introduced in \cite{Wong:2013gua,Cardy:2016fqc}, and re-derive the \TTbar entanglement entropy using the $\mrm{CFT}_2$ modular flow at the \mbox{codim-2} cutoff surface (line). \sidenote{[relation with partial entanglement entropy?]}

	\item[] On the bulk side,

@@

	\item We look at the flow at constant cutoff $z = z_c$, which has non-trivial $\pdd{z}$ component, which in turn leads to a violation of the $2\pi$ periodicity for $\xi$ along the horizon. This could be related to the violation of boosted strong subadditivity (boosted SSA) in \cite{Lewkowycz:2019xse}. \sidenote{We should probably look at the boosted interval.}

@@

	\item We map the the modular flow in the Poincar\'e $\mrm{AdS}_3$ vacuum to the BTZ background, and compute the entanglement entropy as gravitational charge. 
	We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}. This agrees with the finite temperature result we've obtained on the field theory side.

	\item The bulk calculation provides an intuitive explanation of the generalized local temperature trick. \sidenote{Details to be understood.}

@@

{\color{red}\itshape Review TTbar and cutoff AdS. }

\subsection{Black spectrum from gravitional charges}
	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.

@@

@@

	Gravitational entropy is the Noether charge $Q_\xi$ associated with some horizon generator $\xi$. In the case of entanglement entropy between a simple interval and its complement, its corresponding modular flow in the bulk is precisely the horizon generator of the Rindler patch. We can then compute the charge variation using the covariant formula \eqref{charges}.

	Again, to compute $\var{Q}$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions. There is no free parameter in Poincar\'e $\mrm{AdS}_3$, unless we turn on temperature; namely we have to start with the BTZ geometry.
